The Hyperedge Event Model

### 2018-09-07 paper/revision1/HEM-reply.tex
revision plan added

\newpage

@@

>>>>

@@

\newpage
\begin{center}

	\textbf{Revision Plans}
\end{center}
\begin{enumerate}
	\item Section 1: Literature review
	\begin{itemize}
		\item Bomin: add literature review on Perry and Wolfe (2013) arxiv version and comment how our model differs from point process based models (AE1 bullet 2)
		\item Bruce: add literature review on the general class of dynamic network inference including temporal ERGMS and dynamic latent variable models (R1 comment 2)
	\end{itemize}
	\item Section 2: Generative process
		\begin{itemize}
			\item Bomin: change few notations and add notation table in Appendix (AE1 bullet 1)
			\item Bruce: overall rewriting such as rephrasing or clarification (R1 comment 3 \& AE1 bullet 1, minor ones already resolved)
		\end{itemize}
			\item Section 3: Inference
			\begin{itemize}
		\item Bomin: add more MH details and add a subsection 3.2 for computational issues---e.g., complexity and limitations (R1 comment 4, 5 \& AE1 bullet 4)
				\item Bruce: check the added subsection 3.2 and revise
			\end{itemize}
			\item Section 4: Application
			\begin{itemize}
				\item Bomin: re-run PPE considering conditional dependence (section 4.2) and update results \& interpretations in 4.2 \& 4.4 (R1 comment 6 \& AE1 bullet 2)
				\item Bruce: add why direct comparison with SAOMs not possible and come up with better idea than random guess...? (R1 comment 6)
			\end{itemize}

				\item Section 5: Conclusion
				\begin{itemize}
					\item Bruce: possibly further discussing our contribution in the light of alternatives added in the literature review (R1 comment 2)
				\end{itemize}

					\item Bibliography
					\begin{itemize}
						\item Bomin: tons of issues but somehow changes are not reflected...? Double check! (R1 comment 1)
					\end{itemize}

					\item Discuss: sensitivity analysis?					
\end{enumerate}
